Fully structured proof theory for intuitionistic modal logics

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
correction of spacing

%
We obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic in this formalism. 
%
Most rules are similar to the ones of Simpson~\cite{simpson1994}, but some are more explicitly in correspondence with the semantics by using the preorder atoms. 
%
For instance, the rules introducing the $\BOX$-connective correspond to the definition~\eqref{eq:box}.
%
Furthermore, our system has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
%
%As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:

@@

Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule:\vspace*{-.2cm}
%
%For example, you can add the following rule:
$$\small
\vlinf{\rn{4}}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
%to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
%$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.

>>>>

%
We obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic in this formalism. 
%
Most rules are similar to the ones of Simpson~\cite{simpson1994}, but some are more explicitly in correspondence with the semantics by using the preorder atoms. 
%
For instance, the rules introducing the $\BOX$-connective correspond to~\eqref{eq:box}.
%
Furthermore, our system must incorporate the conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and rules $\rn{refl_\le}$ and $\rn{trans_\le}$ are necessary to ensure that the preorder atoms behave as a preorder on labels.
%
%As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:

@@

Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule:\vspace*{-.2cm}
%
%For example, you can add the following rule:
$$\small
\vlinf{\rn{trans}_\rel}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
%to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
%$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
